Revisiting the impact of deepfake technology towards viewer's political choice: A replication of Soubhik Barari (2021)

### 2021-03-18 outputs/paper/paper.Rmd
update results

```{r postfavor, fig.cap="Distribution of feelings towards Sanders in six different situations",echo=FALSE}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Warren)

@@

```{r diagnostic, fig.cap = "Regression diagnostics", echo=FALSE, warning=FALSE, fig.width=10, fig.height=10}
par(mfrow = c(2, 2))
plot(model)
```

@@

### Deception Level
In the descriptive analysis aspect, Table \@ref(tab:table1), shown below, illustrates the average deception level of each media format. The result shows that although deepfake videos have an average deception level of 3.23 out of 5, it is lower than the average level of audio(3.35) and text(3.30). Audio has the highest average deception level, and skit (2.57) has the lowest average deception level.

```{r table1,tab.cap="Average deception level of each media format", echo = FALSE,warning=FALSE}
#Average deception level by treat
EDA%>%
  group_by(treat)%>%
  filter(treat != "control")%>%
  summarise("Average Deception Level"=mean(believed_true,na.rm = T))%>%
  knitr::kable(caption = "Average deception level of each media format")
```

In the statistical analysis aspect, unpaired two-sample t-tests were applied to test whether deepfake videos are statistically different from other media formats at the deception level. The results from Table \@ref(tab:ttest1) to Table \@ref(tab:ttest3) show that only the difference in the deception level between video and skit is significant (p<0.01). The p-values for comparing video and text, video and audio are larger than 0.05, which means there is not sufficient evidence to support that video is different from the audio or text. In other words, videos do not differ from audio or text significantly.

@@

### t-test 2

@@

### t-test 3

@@

### t-test 4

@@

As shown in the summary table, only 9 variables are significant (p<0.05) to the affect level to Elizabeth Warren which are postgraduate education level is; income ranging in $100k to $150k; living in the Northeast of  US; whether age older  than 65; partisan; ambivalent sexism; and treat is advertisement.

@@

In addition, in the Scale-Location plot (Figure \@ref(fig:figure1) in Appendix), an approximately horizontal line is shown, which means the residuals are randomly distributed and have constant variance. The Normal QQ-plot (Figure \@ref(fig:figure2) in Appendix) shows almost all the residuals match the diagonal line, meaning the residuals are normally distributed. The Residual versus Leverage plot (Figure \@ref(fig:figure3) in Appendix) shows that there is no evidence of outliers, and none of the points come close to having both high residual and leverage.

@@

## Appendix B {#appendixB}
```{r figure1,fig.cap="Scale-Location plot", echo=FALSE, warning =FALSE, fig.width=10, fig.height=10}
plot(model,which = 3)
```

## Appendix C {#appendixC}
```{r figure2,fig.cap="Normal QQ-plot", echo=FALSE, warning =FALSE, fig.width=10, fig.height=10}
plot(model,which = 2)
```

## Appendix D {#appendixD}
```{r figure3,fig.cap="Residual versus Leverage plot", echo=FALSE, warning =FALSE, fig.width=10, fig.height=4}
plot(model,which = 5)
```

>>>>

```{r postfavor, fig.cap="Distribution of feelings towards Warren in six different situations",echo=FALSE,fig.width=5, fig.height=4}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Warren)

@@

```{r diagnostic, fig.cap = "Regression diagnostics", echo=FALSE, warning=FALSE, fig.width=8, fig.height=8}
par(mfrow = c(2, 2))
plot(model)
```

@@

### Deception Level
In the descriptive analysis aspect, Table \@ref(tab:table1)^[ Table \@ref(tab:table1) uses the "plyr" package @cite_plyr to calculate the average deception level for each media condition], shown below, illustrates the average deception level of each media format. The result shows that although deepfake videos have an average deception level of 3.23 out of 5, it is lower than the average level of audio(3.35) and text(3.31). Audio has the highest average deception level, and skit (2.57) has the lowest average deception level.

```{r table1,tab.cap="Average deception level of each media format", echo = FALSE,warning=FALSE}
#Average deception level by each media condition except the control group

EDA%>%
  filter(treat !='control')%>%
  ddply(.(treat), summarize,  "Average Deception Level"=round(mean(believed_true,na.rm = T),2))%>%
  knitr::kable(caption = "Average deception level of each media format")
```

In the statistical analysis aspect, unpaired two-sample t-tests were applied to test whether deepfake videos are statistically different from other media formats at the deception level. The results from Table \@ref(tab:ttest1) to Table \@ref(tab:ttest3)^[Table \@ref(tab:ttest1) to Table \@ref(tab:ttest3) use 'KableExtra' @citekableExtra to modify the table style and add title] show that only the difference in the deception level between video and skit is significant (p<0.01). The p-values for comparing video and text, video and audio are larger than 0.05, which means there is not sufficient evidence to support that video is different from the audio or text. In other words, videos do not differ from audio or text significantly.

@@

@@

@@

@@

As shown in the summary table,Table \@ref(tab:modelsummary)^[The 'modelsummary' package @cite_modelsummary was helped to create the table.], there are 12 variables are significant (p<0.05) to the affect level to Elizabeth Warren which are postgraduate education level is; income ranging in $100k to $150k; income ranging larger than $150k; living in the Northeast of  US; whether age older  than 65; partisan; ambivalent sexism; treat is advertisement;treat is audio; treat is skit; and internet usage.

@@

In addition, in the Scale-Location plot (Figure \@ref(fig:diagnostic)), an approximately horizontal line is shown, which means the residuals are randomly distributed and have constant variance. The Normal QQ-plot (Figure \@ref(fig:diagnostic)) shows almost all the residuals match the diagonal line, meaning the residuals are normally distributed. The Residual versus Leverage plot (Figure \@ref(fig:diagnostic)) shows that there is no evidence of outliers, and none of the points come close to having both high residual and leverage.

@@
